\tool: A Multi-Mode Attack Model of BadUSB

### 2021-01-23 WOOT/Files/badusb.tex

We also assume the victim's device is equipped with fully functional USB 3.x protocol and USB Type C connector. As the USB 3.x standard is more and more common around the world, this assumption can be easily fulfilled especially in recent devices.
\subsection{Motivation}
\noindent\outline{Limitation of Rubber Ducky}\\
\outline{Our functionality different mode listing?}\\
\hongyi{The following mode is to be further decided}
\outline{Automatic Scripting Mode}\\
\outline{Remote Control Mode}\\
\outline{OCR/QR Recognition Mode}\\
As we introduced in the Section~\ref{sec:related_work}, there are plenty of existing work \shuqing{Add citation} focusing on BadUSB attack. 
Many of these take advantage of the \textit{trust-by-default} policy of PC, pretend normal HID devices and utilize USB protocol to perform attacks. 
However, these attacks suffer from various drawbacks:
\ding{182} attackers can only simulate limited types of devices such as HIDs (like keyboards and mice) and disks, which makes the attacks less effective;
\ding{183} accurate attacks couldn't be performed due to lack of user interface (UI).
Whatever HID the attackers simulate their USB devices to be, they couldn't obtain the UI to check the current situation, which makes it nearly impossible to locate their attacks precisely or confirm the effects after attacks.

In this work, we utilized the new features of USB 3.x \cite{usb31} \cite{usb32} to address the problems above.
Benefiting from latest protocol, we simulated video card and thus obtained the video stream to perform accurate attacks.

\subsection{Implementation}
\noindent\hongyi{The following mode is to be further decided}\\
\outline{DETAIL of each mode}\\
\outline{Automatic Scripting Mode}\\
\outline{Remote Control Mode}\\
\outline{OCR/QR Recognition Mode}\\
Though Rubber Ducky\cite{rubber} emulates as a HID device enabling various arbitrary execution attacks, fetching feedback from the victim is much more limited. Based on this restriction several defense mechanisms were proposed  like GoodUSB\cite{tian2015defending}\hongyi{We need more example}. These defense mechanism implemented a CAPTCHA-like\cite{captcha} procedure, which requires user to complete certain challenges when a unknown HID device is plugged in. As the Rubber Ducky is only able to emulate HID device, by no means the Rubber Ducky can bypass it. Our \tool, on the other hand, is capable of bypassing this type of defense. Taking advantage of USB 3.x\cite{usb31}\cite{usb32}, \tool can fetch the video stream of the victim and complete the challenge automatically or manually. Moreover, with video capability, our \tool achieved multiple new threat model and are tested under various scenarios.

As there were various Rubber Ducky implementation available, we only focus on its core functionality and our extension. In this section, we first introduce the hardware components we used to build \tool, then we focus on the three different attack modes we implement  for various scenario.

\subsubsection{Attack Model}
The components in our attack model are as follows and the relation between them is illustrated at Fig.~\ref{fig:attack_model}
\begin{itemize}
	\item\textit{USB 3.x Hub} exports the USB 3.x connector into various ports, like DisplayPort, USB 2.0 port etc.
	\item\textit{Video Capture Card} convert DisplayPort signal into UVC-compatible\hongyi{citation needed} data, which is later processed by embedded computer.
	\item\textit{Single Board Computer} processes video stream from the victim where private data is extracted and transmitted through GSM/WiFi.
	\item\textit{HID Emulator} emulates HID device which can be controlled from either the embedded computer.
\end{itemize}
\begin{figure}[t]
	\centering
	\includegraphics[width=0.75\linewidth]{./Figs/attack_model.png}
	\caption{Attack Model}\shuqing{Need to be more compact.}
	\label{fig:attack_model}
\end{figure}
\textbf{Scripting Mode} This mode majorly relies on the ``HID Emulator'' to send constructed HID packet to the victim. These constructed HID packet will be interpreted by the victim as valid key strokes and mouse moves. Thus the attacker can executes arbitrary scripts on the victim's device. This is the function of the original BadUSB. Based on this, we made the following improvement.

First \tool supports defense mechanism bypass. As the original Rubber Ducky cannot get feedback from the victim, defense mechanism like GoodUSB \cite{tian2015defending} is sufficient to prevent these BadUSB attack. But such defense mechanism needs visual notification to request authentication for unknown USB device. This means that when the defense request authentication from the user, our \tool is able to capture the content of authentication challenge and complete it. After the defense is bypassed, \tool continues the emulation and script execution, resulting a successful attack.

Moreover, as the mouse relies on the visual feedback to work properly, its emulation and automation were not supported by the original version of Rubber Ducky. Yet with the video output support from USB 3.x, our \tool implements full-functional mouse emulation. This function enables attacks toward pure GUI programs and showed great potential in mobile attack scenario. Details can be obtained in Section~\ref{sec:experiment}.

The advantage of this mode is that it archives defense bypass and attack feedback with low overhead. As mentioned above, we only require video stream at the begin(defense bypass) and the end(feedback) of the attack. Moreover, with mouse supported, \tool extends the original BadUSB attack surface and perform well in mobile device.

\textbf{Privacy Extraction Mode}
\tool under this mode does not emulate other USB device and solely relies on the video stream function of USB 3.x and use ``Video Capture'' component to deliver the stream to the embedded computer. The victim's device will mistakenly treat \tool as a external monitor and try to output its video stream. This stream is latter processed by the embedded computer to extract private data.

@@

\textbf{Remote Control Mode}
In \tool, we have implemented all components required to control a computer/mobile remotely, including a video stream, keyboard/mouse emulation. Thus with all components enabled, not only will the victim's device treat \tool as a external display, but also a valid HID input source. Hence we can archive complete hijack of victim's device.

\tool under this mode follows a simple logic. \tool will receive video stream from the victim's device and redirect it to the attacker via GSM/WiFi. In the meanwhile, \tool also receives commands from the attacker through GSM/WiFi and replay them to the victim by USB emulation.

This mode enable attacker to perform delicate operation that is beyond automation. Moreover, this mode provides a backdoor that does not require host network and thus is undetectable by firewall running on the host machine.
\hongyi{I think this is a quite good selling point?}\shuqing{Agree with Hongyi.}

The advantage of this mode is that it can completely hijack the victim device. But this complete control also comes with the price of high power consumption and risk of being detected by the user.

>>>>

We also assume the victim's device is equipped with fully functional USB 3.x protocol and USB Type C connector. As the USB 3.x standard is more and more common nowadays, this assumption can be easily fulfilled especially in recent devices.
\subsection{Motivation}
\noindent\outline{Limitation of Rubber Ducky}\\
\outline{Our functionality different mode listing?}\\
\hongyi{The following mode is to be further decided}
\outline{Automatic Scripting Mode}\\
\outline{Remote Control Mode}\\
\outline{OCR/QR Recognition Mode}\\
As we introduced in the Section~\ref{sec:related_work}, there are plenty of existing work \shuqing{Add citation} focusing on BadUSB attack. 
Many of these take advantage of the \textit{trust-by-default} policy of PC, pretend to be normal HID devices and utilize USB protocol to perform attacks. 
However, these attacks suffer from various drawbacks:
\ding{182} attackers can only simulate limited types of devices such as HIDs (like keyboards and mice) and disks, which makes the attacks less effective;
\ding{183} accurate attacks couldn't be performed due to lack of user interface (UI).
Whatever HID the attackers simulate their USB devices to be, they couldn't obtain the UI to check the current situation, which makes it nearly impossible to carry out their attacks precisely or confirm the effects after attacks.

In this work, we utilized the new features of USB 3.x \cite{usb31} \cite{usb32} to address the problems above.
Benefiting from latest protocol, we simulated external display and thus obtained the video stream to perform accurate attacks.

\subsection{Implementation}
\noindent\hongyi{The following mode is to be further decided}\\
\outline{DETAIL of each mode}\\
\outline{Automatic Scripting Mode}\\
\outline{Remote Control Mode}\\
\outline{OCR/QR Recognition Mode}\\
Though BadUSB devices\cite{badusb} like Rubber Ducky\cite{rubber, rubberducky2020} emulates as a HID device enabling various arbitrary execution attacks, fetching feedback from the victim is much more limited. Based on this restriction, several defense mechanisms were proposed  like GoodUSB\cite{tian2015defending}. These defense mechanism implemented a CAPTCHA-like\cite{captcha} procedure, which requires user to complete certain challenges when a unknown HID device is plugged in. As the BadUSB is only able to emulate a limited kind of devices like HID or disks, by no means the BadUSB can bypass it. Our \tool, on the other hand, is capable of bypassing this type of defense. Taking advantage of USB 3.x\cite{usb31}\cite{usb32}, \tool can fetch the video stream of the victim and complete the challenge manually by the attacker. Moreover, with video capability combined with traditional BadUSB, our \tool achieved multiple new attack paradigm and are tested under various real-life scenarios.

As there were various BadUSB implementations available, we only focus on its core functionality and our extension. In this section, we first introduce the components we used in \tool, then we focus on the three different attack modes we implement  for different scenarios.

\subsubsection{Attack Model}
The components in our attack model are as follows and the relation between them is illustrated at Fig.~\ref{fig:attack_model}
\begin{itemize}
	\item\textit{USB 3.x Hub} exports the USB 3.x connector into various ports, like DisplayPort, USB 2.0 port etc.
	\item\textit{Video Capture Card} convert DisplayPort signal into UVC-compatible\hongyi{citation needed} data, which is later processed by embedded computer.
	\item\textit{Single Board Computer} processes video stream from the victim where private data is extracted and transmitted via GSM/WiFi to the attacker.
	\item\textit{HID Emulator} emulates HID device which can be controlled from the attacker.
\end{itemize}
\begin{figure}[htbp]
	\centering
	\includegraphics[width=0.75\linewidth]{./Figs/attack_model.png}
	\caption{Attack Model}\shuqing{Need to be more compact.}
	\label{fig:attack_model}
\end{figure}
\textbf{Scripting Mode} This mode majorly relies on the ``HID Emulator'' to send constructed HID packet to the victim. These constructed HID packet will be interpreted by the victim as valid keystrokes and mouse moves. Thus the attacker can executes arbitrary scripts on the victim's device. This is the function of the original BadUSB. Based on this, we made the following improvement.

First \tool supports defense mechanism bypass. As the original BadUSB cannot get feedback from the victim, defense mechanism like GoodUSB \cite{tian2015defending} is sufficient to prevent these BadUSB attack. But such defense mechanism needs visual notification to request authorization for unknown USB device. This means that when the defense request authorization from the user, our \tool is able to capture the content of authorization challenge and complete it. After the defense is bypassed, \tool continues the emulation and script execution, resulting a successful attack.

Moreover, as the mouse relies on the visual feedback to work properly, its emulation and automation were not supported by the original version of BadUSB. Yet with the video output support from USB 3.x, our \tool implements full-functional mouse emulation. This function enables attacks toward pure GUI programs and showed great potential in mobile attack scenario. Details can be obtained in Section~\ref{sec:experiment}.

The advantage of this mode is that it archives defense bypass and attack feedback with low overhead. As mentioned above, we only require video stream at the begin(defense bypass) and the end(result feedback) of the attack. Moreover, with mouse supported, \tool extends the original BadUSB attack surface and perform well in mobile device.

\textbf{Privacy Extraction Mode}
\tool under this mode does not emulate other USB device and solely relies on the video stream function of USB 3.x and use ``Video Capture'' component to transmit the stream to the embedded computer. The victim's device will mistakenly treat \tool as a external monitor and try to output its video stream. This stream is latter processed by the embedded computer to extract private data.

@@

\textbf{Remote Control Mode}
In \tool, we have implemented all components required to control a computer/mobile remotely, including a video stream and a keyboard/mouse emulation. Thus with all components enabled, not only will the victim's device treat \tool as a external display, but also a valid HID input source. Hence we can archive complete hijack of victim's device.

\tool under this mode follows a simple logic. \tool will receive video stream from the victim's device and redirect it to the attacker via GSM/WiFi. In the meanwhile, \tool also receives keystrokes and mouse movement from the attacker through GSM/WiFi and replay them to the victim by USB emulation.

This mode enable attacker to perform delicate operation that is beyond automation. Moreover, this mode provides a backdoor that does not require host network and thus is undetectable by the firewall running on the host machine.
\hongyi{I think this is a quite good selling point?}\shuqing{Agree with Hongyi.}

The advantage of this mode is that it can completely hijack the victim device and provide a backdoor beyond detection of firewalls. But this complete control also comes with the price of high power consumption and risk of being detected by the user.
